\section{Working Experience}

\cventry{2024--Current}{Senior Software Engineer}{Asan Pardakht}{Tehran, Iran}{}{%
  \begin{itemize}
    \item Managed application layout configuration for over 50 million users using AppConfig. Implemented features to synchronize and enforce updates on specific UI components, tailored to diverse user policies.
    \item Designed and maintained an SMS Gateway, critical for payment services and user authentication. also Developed a Kubernetes operator to streamline the definition and management of SMS templates.
    \item Maintained and enhanced the Discount Service, enabling users to access offers such as ticket purchases. Built and maintained a back-office system for seamless management.
    \item Developed and maintained the Profile Service, supporting approximately 50 million users. Implemented subscription management with integrated payment processing via EasyPay IPG.
    \item Monitored system performance and created Grafana dashboards for these systems, providing detailed insights and actionable metrics to ensure smooth operations and rapid issue resolution.
  \end{itemize}
}

\cventry{2023--2024}{Software Engineer}{Sotoon / Hezardastan}{Tehran, Iran}{}{%
  \begin{itemize}
    \item Contributed to the development of internal operators to manage compute resources and their communication with other resources.
    \item Design, implement and maintain a Private Cloud Infrastructure by using OpenStack.
    \item Writing different k8s webhooks for various purposes.
    \item Writing complicated integration, functional and unit tests with high coverage to test the whole system and to make sure operators can correctly perform their tasks.
    \item Prepare an isolated container with DockerInDocker to hold a k8s cluster in it and bringup openstack via openstack-helm and use this container inside CI/CD pipeline to perform jobs and also as a neat solution to perform our daily tasks in it.
  \end{itemize}
}

\cventry{2021--2023}{Software Engineer}{Snapp!}{Tehran, Iran}{}{%
  \begin{itemize}
    \item Designing and Implementing the in-app-call project named heliograph by designing real-time services including webRTC via Pion.
    \item Monitor and develop message-brokers like EMQX, NATS, kafka, rabbitmq and etc.
    \item Coporating in snapp-cloud for developing cloud-native projects by writing kubernetes operators.
    \item Participating in deploying and monitoring services using K8S, Grafana, and ELK.
    \item Experienced in working with Jira management tools and Confluence page development.
    \item Helped junior engineers to improve their productivity by mentoring them and supporting colleagues.
    \item Design, implementation, and maintenance of k8s cluster via OpenShift in 5 zones and 2 regions and supporting more than 500 engineers with +200 production applications.
    \item Orchestrated infrastructure and automated operations using Ansible, Terraform, and Helm.
    \item Contributed to the development of internal operators to manage some custom resources and reduce manual work in Go.
    \item Worked with CI/CD pipelines via Gitlab-CI to deploy our changes on OpenShift/Kubernetes and check Ansible and Terraform syntax.
  \end{itemize}
}

\cventry{2019--2021}{Full Stack Developer - Founder}{Melodyo}{Tehran, Iran}{}{%
  \begin{itemize}
    \item Develop a Web Scrapper for scrapping music files from various music websites
    \item Using ffmpeg API in Go to generate different bit-rates of the musics.
    \item Develop monitoring dashboards and enhance performance of the backend.
    \item Experience with realtime streaming
    \item Architect \& develop mobile client with Flutter and work with background services, building audio, video and downloader services.
  \end{itemize}
}
